Reinforcement Learning Produces Dominant Strategies for the Iterated Prisoner's Dilemma

### 2017-07-08 main.tex
Remove duplicates from bibliography.

The library is continuously developed and as of version 3.0.0, the library
contains over 200 strategies, many from the scientific literature, including
classic strategies like Win Stay Lose Shift \cite{nowak1993strategy} and
previous tournament winners such as OmegaTFT \cite{slany2007some}, Adaptive
Pavlov \cite{li2007design}, and ZDGTFT2 \cite{stewart2012extortion}.

@@

In this work we describe how collections of strategies in the Axelrod library
have been used to train new strategies specifically to win IPD tournaments.
These strategies are trained using generic strategy archetypes based on e.g.\
finite state
machines, arriving at particularly effective parameter choices through
evolutionary or particle swarm algorithms. There are several
previous publications that use evolutionary algorithms to
evolve IPD strategies in various circumstances
\cite{ashlock2006training, ashlock2015multiple, ashlock2006changes,
      ashlock2014shaped, ashlock2014evolution, barlow2015varying,
      fogel1993evolving, marks1989niche, sudo2015effects,
      vassiliades2010multiagent}. See also \cite{gaudesi2016exploiting} for a
strategy trained to win against a collection of well-known IPD opponents and see
\cite{franken2005particle} for a prior use of particle swarm algorithms. Our
results are unique in that we are able to train against a large collection of
well-known strategies available in the scientific literature. Crucially, the
software used in this work is openly available and can be used to train strategies
in the future in a reliable manner, with confidence that the opponent strategies
are correctly implemented, tested and documented.
Moreover, as of the time of writing,
we claim that this work contains the best known strategies for the iterated
prisoner's dilemma.

@@

Using a numerical method of fingerprinting based on
\cite{ashlock2008fingerprinting, ashlock2009fingerprint} we can compare
strategies. The fingerprints of the top performing standard strategies are shown
in Figures~\ref{fig:comparison_fingerprint_standard}. There is a striking
similarity in the fingerprints.

>>>>

The library is continuously developed and as of version 3.0.0, the library
contains over 200 strategies, many from the scientific literature, including
classic strategies like Win Stay Lose Shift \cite{nowak1993strategy} and
previous tournament winners such as OmegaTFT \cite{slany2007some}, Adaptive
Pavlov \cite{li2007design}, and ZDGTFT2 \cite{Stewart2012}.

@@

In this work we describe how collections of strategies in the Axelrod library
have been used to train new strategies specifically to win IPD tournaments.
These strategies are trained using generic strategy archetypes based on e.g.\
finite state
machines, arriving at particularly effective parameter choices through
evolutionary or particle swarm algorithms. There are several
previous publications that use evolutionary algorithms to
evolve IPD strategies in various circumstances
\cite{ashlock2006training, Ashlock2015, Ashlock2006,
      ashlock2014shaped, Ashlock2014, barlow2015varying,
      fogel1993evolving, marks1989niche, sudo2015effects,
      vassiliades2010multiagent}. See also \cite{Gaudesi2016} for a
strategy trained to win against a collection of well-known IPD opponents and see
\cite{franken2005particle} for a prior use of particle swarm algorithms. Our
results are unique in that we are able to train against a large collection of
well-known strategies available in the scientific literature. Crucially, the
software used in this work is openly available and can be used to train strategies
in the future in a reliable manner, with confidence that the opponent strategies
are correctly implemented, tested and documented.
Moreover, as of the time of writing,
we claim that this work contains the best known strategies for the iterated
prisoner's dilemma.

@@

Using a numerical method of fingerprinting based on
\cite{Ashlock2008, ashlock2009fingerprint} we can compare
strategies. The fingerprints of the top performing standard strategies are shown
in Figures~\ref{fig:comparison_fingerprint_standard}. There is a striking
similarity in the fingerprints.
